Compare pseqs

### 2019-05-24 comparepseqs.Rmd
Delete quit
list cast mistake
Beta saved over alpha

```{r install, eval = FALSE, include = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite("BiocInstaller")
library(BiocInstaller)
source("http://www.bioconductor.org/biocLite.R")
biocLite("microbiome")
```

@@

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[[subset.run]]
}

message(rds)
quit()
```

@@

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(pseq) %>%
        mutate(diversities_shannon = scale(diversities_shannon))

    alphadiversity <- list(min =  calculateglm(dset, modelstring = fo.alpha.min),
                           full = calculateglm(dset, modelstring = fo.alpha.full))

    saveRDS(alphadiversity,
            file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

    bray.dist.matrix <- calculate.beta.matrix(pseq)

    saveRDS(bray.dist.matrix,
            file = paste0("rds-comparepseqs/bray-", key , ".rds"))

    betadiversity <- list(min = calculateadonis(dset = dset,
                                                matrix = bray.dist.matrix,
                                                covariates = covariates.min,
                                                npermutations = 1000),
                          full = calculateadonis(dset = dset,
                                                 matrix = bray.dist.matrix,
                                                 covariates = covariates.full,
                                                 npermutations = 1000))

    saveRDS(betadiversity,
            file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

@@

for (key in names(rds)) {
    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])

>>>>

```{r install, eval = FALSE, include = FALSE}
install.packages("BiocManager")
BiocManager::install("phyloseq")

source("https://bioconductor.org/biocLite.R")
biocLite("BiocInstaller")
library(BiocInstaller)
source("http://www.bioconductor.org/biocLite.R")
biocLite("microbiome")
```

@@

```{r rds subset, eval = FALSE}
subset.run <- 3
```

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[subset.run]
}
```

@@

for (key in names(rds)) {
    missing = list()

    if (!file.exists(paste0("rds-comparepseqs/alpha-", key , ".rds"))) {
        missing$alpha = TRUE
    } else {
        alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alpha-", key , ".rds"))
    }

    if (!file.exists(paste0("rds-comparepseqs/bray-", key , ".rds"))) {
        missing$bray = TRUE
    } else {
        bray.dist.matrix <- readRDS(file = paste0("rds-comparepseqs/bray-", key , ".rds"))
    }

    if (!file.exists(paste0("rds-comparepseqs/beta-", key , ".rds"))) {
        missing$beta = TRUE
    } else {
        betadiversity <- readRDS(file = paste0("rds-comparepseqs/beta-", key , ".rds"))
    }

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = scale(diversities_shannon))

        if ("alpha" %in% names(missing)) {
            alphadiversity <- list(min =  calculateglm(dset, modelstring = fo.alpha.min),
                                   full = calculateglm(dset, modelstring = fo.alpha.full))
            saveRDS(alphadiversity, file = paste0("rds-comparepseqs/alpha-", key , ".rds"))
        }

        if ("bray" %in% names(missing)) {
            bray.dist.matrix <- calculate.beta.matrix(pseq)
            saveRDS(bray.dist.matrix, file = paste0("rds-comparepseqs/bray-", key , ".rds"))
        }

        if ("beta" %in% names(missing)) {        
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

@@

for (key in names(rds)) {
    alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])
